\section{Introduction}
\label{sec:introduction}

% \todo[inline]{Mention to CGTY result anyways.}
% \todo[inline]{Move the SCC convexity question to the intro.}
% \todo[inline]{Could bias random walk in one sided region to prove stronger SCC results}
% \todo[inline]{Add ``A Mirzakhani recursion for non-orientable surfaces'' reference}

% {\color{red} Outline of introduction.}
% \begin{enumerate}[(i)]
% \item List similarities with IVGF surfaces, and point out where analogy breaks down.
% \item State theorem about systole being weak convex.
% \item Weak convexity lets us focus on systole, rather than entire space.
% \item Can prove exponential rareness of thin geodesics in systole, using random walk methods.
% \item Using this, we get stat-convex, and consequently, rest of PS theory thanks to others.
% \item Mention why we might care.
% \item Hard part of random walk argument is showing hLP = hNP. We spend sections 5 and 6 doing this.
% \item Sketch out idea of proof of hLP = hNP.
% \item Mention what's in the appendix.
% \end{enumerate}

Mapping class groups $\mcg(\no_g)$ of non-orientable surfaces $\no_g$ have many similarities to infinite covolume geometrically finite Fuchsian groups, in a manner similar how mapping class groups of orientable surfaces sometimes behave like lattices in $\mathrm{SL}_2(\mathbb{R})$.

\begin{enumerate}[(i)]
\item The mapping class groups $\mcg(\no_g)$ are finitely presented.
\item The action of $\mcg(\no_g)$ on the Teichmüller space $\teich(\no_g)$ has infinite $\nu_N$-covolume, where $\nu_N$ is the generalization of the Weil-Petersson volume form on Teichmüller spaces of non-orientable surfaces (\cite[Theorem 17.1]{gendulphe2017whats} and \cite{norbury2008lengths}).
\item The limit set of $\mcg(\no_g)$ in the Thurston boundary of $\teich(\no_g)$ is $\pml^+(\no_g)$, i.e.\ the projective measured laminations that have no two-sided components  (\cite{erlandsson2023mapping} and \cite{limitsetkhan}), which is a subset of the boundary with zero Lebesgue measure (\cite{norbury2008lengths}).
\item The Teichmüller geodesic flow is not ergodic with respect to any Borel measure on the unit cotangent bundle with full support (\cite[Proposition 17.5]{gendulphe2017whats}).
\item There exists an $\mcg(\no_g)$-equivariant deformation retract of $\teich(\no_g)$ to $\systole(\no_g)$, the subset where no one-sided curve is shorter than $\vept > 0$. The action of $\mcg(\no_g)$ on $\systole(\no_g)$ is finite $\nu_N$-covolume \cite[Proposition 19.1]{gendulphe2017whats}.
\end{enumerate}

With these similarities, one might expect that $\systole(\no_g)$ serves as a convex core of $\teich(\no_g)$, and the geodesic flow restricted to tangent directions whose forward and backward end points lie in the limit set will be ergodic, with respect to a finite geodesic flow invariant measure supported only on these tangent directions.

A prior result of the author shows that this is not the case: $\systole(\no_g)$ is not even quasi-convex, i.e.\ geodesic segments whose endpoints lie in $\systole(\no_g)$ can travel arbitrarily far from $\systole(\no_g)$.

\begin{theorem}[Theorem 5.2 of \cite{limitsetkhan}]
  For all $\vept > 0$, and all $D > 0$, there exists a Teichmüller geodesic segment whose endpoints lie in $\systole(\no_g)$, such that some point in the interior of the geodesic segment is more than distance $D$ from $\systole(\no_g)$.
\end{theorem}

However, we show that this failure of quasi-convexity is not a serious obstruction to understanding geodesic segments whose endpoints lie in $\systole(\no_g)$.

\begingroup
\def\thetheorem{\ref{thm:weak-convexity}}
\begin{theorem}
  For any $\vepd > 0$, there exists constants $\vept^{\prime}$ and $c$, such that any geodesic segment $\gamma$, whose length is more than $c$, with endpoints in $\systole(\no_g)$, for $0 < \vept < \vept^{\prime}$, can be homotoped to a segment relative to endpoints to lie entirely within $\systole(\no_g)$, such that the length of the homotoped segment $\gamma^{\prime}$ satisfies the following inequality.
  \begin{align*}
    \ell(\gamma^{\prime}) \leq \ell(\gamma) \cdot (1 + \vepd)
  \end{align*}
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup
% \todo[inline]{Should not have $\vept$ and constant $t$ in the same theorem statement.}

Theorem \ref{thm:weak-convexity} shows that $\systole(\no_g)$, despite not being convex, almost behaves like the convex core of $\teich(\no_g)$: it is a metric subset of $\teich(\no_g)$ (with respect to the induced path metric) which is distorted by an arbitrarily small amount.
We call $\systole(\no_g)$ the \emph{weak convex core} of $\teich(\no_g)$, and focus our attention on this subspace as a metric space, where the metric is the induced path metric, which we denote by $d_{\vept}$ (in all of our results that follow, we are using this metric on $\systole(\no_g)$, and not the Teichmüller metric).
If we restrict our attention to the cotangent directions in $\teich(\no_g)$ along which the geodesic flow does not eventually leave $\systole(\no_g)$, we can use those cotangent directions to define a geodesic flow for $\systole(\no_g)$.
We call this collection of restricted directions the restricted cotangent bundle over $\systole(\no_g)$.

% If we restrict our attention to the cotangent directions in which the Teichmüller geodesic enters $\systole(\no_g)$ for arbitrarily large times\todo{Is this clear?}, we can define a \emph{slowed-down} geodesic flow on those tangent directions using the geodesic flow in $\teich(\no_g)$.
% This new geodesic flow projects down to $\systole(\no_g)$, and is only slower than the usual Teichmüller geodesic flow by a factor of at most $1 + \vepd$.
% \todo{Might wanna remove it? Or say, ``if we restrict our attention to tangent directions that do not eventually leave systole, we can define a geodesic flow for this new space.''}

In light of this, we restrict our attention to $\systole(\no_g)$, and the $\mcg(\no_g)$ action on $\systole(\no_g)$.
Since the action of $\mcg(\no_g)$ on $\systole(\no_g)$ is finite $\nu_N$-covolume (but not cocompact), one might try to prove that the action is
% \emph{analogous} to
{like}
the action of lattices in $\mathrm{SL}_2(\mathbb{R})$ on $\mathbb{H}$.
However, the results on lattices (and Teichmüller spaces of orientable surfaces) rely on having a measure preserving $\mathrm{SL}_2(\mathbb{R})$ action on the unit tangent bundle (respectively on the moduli space of quadratic differentials), and use the interplay between the geodesic flow and the horocycle flow.

For non-orientable surfaces, we do not have an analog of the horocycle flow on the space of quadratic differentials, so we cannot hope to directly import the techniques from the orientable case.
However, \textcite{10.1093/imrn/rny001} introduced a notion of \emph{statistically convex-cocompact action}, which can replace the notion of a lattice-like action for our setting.
In the setting of $\systole(\no_g)$, proving statistical convex-cocompactness is equivalent to proving that geodesic segments between $\mcg(\no_g)$ orbit points in $\systole(\no_g)$ enter the thin part (i.e.\ the region in $\systole(\no_g)$ where some two-sided curve is short) with low probabilities.

Our main result is that this holds for the $\mcg(\no_g)$ action on $\systole(\no_g)$.
\begin{theorem}[Corollary of Theorems \ref{thm:entropy-equality-implies-scc} and \ref{thm:entropy-equality}]
  \label{thm:statistical-convex-cocompactness}
  The action of $\mcg(\no_g)$ on $(\systole(\no_g), d_{\vept})$ is statistically convex-cocompact.
\end{theorem}
% \todo{Is stating that statistical convexity follows as a corollary of two theorems okay?}

Using Theorem \ref{thm:weak-convexity} and a result of \textcite{minsky1996quasi}, we have that the projection of balls disjoint from axes of the pseudo-Anosov elements have bounded diameter.
This means pseudo-Anosov elements are \emph{strongly contracting} and most reducible elements are not (see Lemma \ref{lem:strongly-contract-class}).

Coulon (\cite{coulon2022patterson}, \cite{coulon2024ergodicity}) and Yang (\cite{10.1093/imrn/rny001}, \cite{yang2020genericity}) prove fairly general results in the setting of statistically convex cocompact group actions with strongly contracting elements.
We state these results in our setting, where $\mcg(\no_g)$ plays the role of the group, $\systole(\no_g)$ is the metric space upon which $\mcg(\no_g)$ acts via a statistically convex cocompact action (and $d_{\vept}$ denotes the distance function), and pseudo-Anosovs play the role of strongly contracting elements.
We also denote balls of radius $R$ with respect to the metric $d_{\vept}$ centered at $p$ as $B_R(p)$.

\begin{theorem}[Purely exponential growth (Theorem B of \cite{10.1093/imrn/rny001})]
  There exist positive constants $A$ and $B$ such that the following bounds hold for the cardinality of the $\mcg(\no_g)$ orbit of a point $p \in \systole(\no_g)$ in a ball of radius $R$.
  \begin{align*}
    A \exp(hR) \leq \#\left( \mcg(\no_g) \cdot p \cap B_R(p) \right) \leq B \exp(hR)
  \end{align*}
  Here, $h$ is the critical exponent for the group action.
\end{theorem}

We also have that pseudo-Anosov elements are exponentially generic with respect to the induced metric on $\systole(\no_g)$.
% (recall that the ratio of this metric to the standard Teichmüller metric is close to $1$)
% .

\begin{theorem}[Exponential genericity of contracting elements (Theorem 1.4 of \cite{yang2020genericity})]
  \label{thm:pure-exponential}
  For a point $p \in \systole(\no_g)$, let $N(R)$ denote the number of mapping class elements $\gamma$ such that $d_{\vept}(p, \gamma p) \leq R$, and let $N_{nc}(R)$ denote the reducible mapping class elements $\gamma$ that leave a two-sided curve invariant, and $d_{\vept}(p, \gamma p) \leq R$.
  Then there exists a positive constant $c$ such that the following holds for large enough $R$.
  \begin{align*}
    \frac{N_{nc}(R)}{N(R)} \leq \exp(-cR)
  \end{align*}
\end{theorem}

After picking a basepoint $p \in \systole(\no_g)$, we can replicate the classical construction of Patterson-Sullivan measures \cite{sullivan1979density} to get a measure $\nu$ supported on the limit set $\pml^+(\no_g)$.
However, for Theorem \ref{thm:hts-dichotomy}, we need to consider the limit set in an alternative compactification, namely the horofunction compactification, and consider the Patterson-Sullivan measure on the limit set in this compactification.
We will abuse notation, and denote the Patterson-Sullivan measure on this limit set by $\nu$ as well.
Since we have that the action is statistically convex cocompact, and we have plenty of strongly contracting elements, the results of Coulon (\cite{coulon2022patterson},\cite{coulon2024ergodicity}) let us say a lot about the Patterson-Sullivan measure $\nu$.
We have the Hopf-Tsuji-Sullivan dichotomy (or rather, the divergent half of the result).

\begin{theorem}[Hopf-Tsuji-Sullivan dichotomy (Theorem 1.1 of \cite{coulon2024ergodicity})]
  \label{thm:hts-dichotomy}
  For the action of $\mcg(\no_g)$ on $\systole(\no_g)$, the following are equivalent.
  \begin{enumerate}[(i)]
  \item The Poincaré series for $\mcg(\no_g)$ diverges at the critical exponent.
  \item The measure $\nu$ gives full measure to the radial limit set.
  \item The diagonal action on $\Lambda \times \Lambda$ is ergodic with respect to the product measure $\nu \otimes \nu$, where $\Lambda$ is the limit set of $\mcg(\no_g)$ in the horofunction boundary.
  \item The geodesic flow on the unit tangent bundle $(\Lambda \times \Lambda \times \mathbb{R})/\mcg(\no_g)$ is ergodic with respect to the Bowen-Margulis measure.
  \end{enumerate}
\end{theorem}

It follows as a corollary of Theorem \ref{thm:pure-exponential} that the Poincaré series for $\mcg(\no_g)$ diverges at the critical exponent, and as a result, we have all the other equivalent criteria that appear in the Hopf-Tsuji-Sullivan dichotomy.

% \begin{remark}
%   Note that the limit set of $\mcg(\no_g)$ in the horofunction boundary is not (necessarily) the same as the limit set in the Thurston boundary, which is known to be $\pml^+(\no_g)$.
%   The horofunction boundary is sensitive to the metric that one uses: in particular that means that looking at $\systole(\no_g)$ with the induced path metric $d_{\vept}$ will give us a possibly different horofunction boundary as opposed to looking at the horofunction boundary of $\systole(\no_g)$ with the Teichmüller metric.


% \end{remark}

\begin{remark}
  % \textcite{coulon2024ergodicity} states the above theorem where the role of boundary is played by the horofunction boundary of the metric space, which for the Teichmüller space is \emph{not} the Thurston boundary $\pml(\no_g)$.
  In practice, it is preferable to work with the Thurston boundary of Teichmüller space rather than the horofunction boundary, since the Thurston boundary is a much better understood object.

  For statistically convex-cocompact actions of subgroups of mapping class groups (with respect to the Teichmüller metric) (see \textcite{gekhtman2023dynamics}, and \textcite{CGTY}), one can replace the horofunction boundary in the statement of the Hopf-Tsuji-Sullivan dichotomy with the Thurston boundary using the following sequence of results.
  % To state conditions (iii) and (iv) of Theorem \ref{thm:hts-dichotomy} for the Thurston boundary, rather than the horofunction boundary, we use the following sequence of results.
  \begin{enumerate}[(i)]
  \item \textcite{miyachi2008teichmuller} proves that there is an $\mcg(\no_g)$ equivariant bijective map between the uniquely ergodic points in the horofunction boundary, and the uniquely ergodic points in the Thurston boundary.
  \item By condition (ii) of the Hopf-Tsuji-Sullivan dichotomy, the radial limit points in the horofunction boundary have full measure.
  \item A geodesic converging to a radial limit point stays within bounded distance of the mapping class group orbit, and by Masur's criterion for unique ergodicity \cite{masur1982interval}, we have that the corresponding limit point in the boundary must be uniquely ergodic.
  \item Consequently, the uniquely ergodic limit points have full measure in the horofunction boundary, and we can thus replace that with the Thurston boundary, since they agree on a full measure subset.
  \end{enumerate}
  % Furthermore, by condition (ii) of the Hopf-Tsuji-Sullivan dichotomy, the radial limit points have full measure, and Masur's criterion gives us that radial limit points are uniquely ergodic.
  % This lets us replace the horofunction boundary with the Thurston boundary in the statement of the result, since they agree on a full measure set.

  In our setting, i.e. the $\mcg(\no_g)$ action on $\systole(\no_g)$ with the $d_{\vept}$ metric, we do not know if there is an $\mcg(\no_g)$-equivariant map between the uniquely ergodic points in the Thurston boundary with a full measure subset of the horofunction boundary.
  We do not even have a very good description of the horofunction boundary of $(\systole(\no_g), d_{\vept})$ in terms of measured foliations on $\no_g$.
  One way to obtain ergodicity of the $\mcg(\no_g)$ action on $\pml^+(\no_g)$ would be to get an affirmative answer to the following question.
\begin{question}[Restatement of Question \ref{ques:full-stat-core}]
  \label{ques:full-scc}
  Is the action of $\mcg(\no_g)$ on $(\teich(\no_g), d_T)$ statistically convex cocompact, where $d_T$ is the Teichmüller metric?
\end{question}
We expect the answer to this question is yes, despite the random walk methods of our proof not working in this setting.
\end{remark}

% In particular, we have that the action of $\mcg(\no_g)$ on the limit set $\pml^+(\no_g)$, and the double limit set $\pml^+(\no_g) \times \pml^+(\no_g)$ is ergodic, and that the geodesic flow is ergodic with respect to the Bowen-Margulis measure.

% {\color{red} Insert the new theorems here.}

% \textcite{gekhtman2023dynamics}, and \textcite{CGTY} (in upcoming work) prove the following theorems about statistically convex cocompact actions of subgroups of mapping class groups on Teichmüller space.

% \begin{theorem}[To appear in \textcite{CGTY}]
%   \label{thm:bms-finite}
%   Let $\Gamma$ be a subgroup of the mapping class group $\mcg(\os_g)$ whose action on $\teich(\no_g)$ is statistically convex-cocompact.
%   Then the Bowen-Margulis measure $\mu_{\mathrm{BMS}}$ on the unit cotangent bundle of $\teich(\os_g)/\Gamma$ is finite.
% \end{theorem}

% \begin{theorem}[Theorem 4.9 of \cite{gekhtman2023dynamics}]
%   \label{thm:mixing-bms}
%   If $\Gamma$ is a subgroup of the mapping class group such that the associated Bowen-Margulis measure is finite, then the geodesic flow is mixing with respect to $\mu_{\mathrm{BMS}}$.
% \end{theorem}

% As a corollary of the Theorem \ref{thm:mixing-bms}, we get the following results about the Patterson-Sullivan measures and the action of $\Gamma$ on the limit set.
% \begin{corollary}
%   \label{cor:niceness}
%   If $\Gamma$ is a subgroup of $\mcg(\os_g)$ such that the Bowen-Margulis measure associated to $\Gamma$ is finite, then the following results hold.
%   \begin{itemize}
%   \item There exists a unique family of conformal densities $\left\{ \mu_x \right\}_{x \in \teich(\os_g)}$ on the limit set of $\Gamma$, given by the Patterson-Sullivan construction.
%   \item The action of $\Gamma$ on the limit set is ergodic.
%   \end{itemize}
% \end{corollary}

% We believe Theorem \ref{thm:bms-finite} also works when we consider the $\mcg(\no_g)$ action on $\systole(\no_g)$ instead of $\teich(\os_{g-1})$ (i.e.\ the Teichmüller space of the orientation double cover), since the proof of Theorem \ref{thm:bms-finite} relies on considering the limit set of the group, which is the same for the action on $\systole(\no_g)$ as it is for the action on the entire Teichmüller space (we proved this in \cite[Theorem 4.2]{limitsetkhan}).

% Combining Theorem \ref{thm:statistical-convex-cocompactness} with Theorems \ref{thm:bms-finite} and \ref{thm:mixing-bms} lets us construct Patterson-Sullivan measures (with good dynamical properties) on the limit set, and a finite Bowen-Margulis measure on the unit cotangent bundle.
% % In particular, \textcite{CGTY} show that the construction of Patterson-Sullivan measures for statistically convex-cocompact subgroups of the mapping class groups leads to a finite geodesic flow invariant measure (i.e.\ the Bowen-Margulis measure) on the tangent bundle, and \textcite{gekhtman2023dynamics} show that finite Bowen-Margulis measure implies mixing of the geodesic flow in this setting.
% In particular, letting $\Gamma = \mcg(\no_g) < \mcg(\os_{g-1})$ gives us a version of Theorem \ref{thm:mixing-bms} and Corollary \ref{cor:niceness} for $\mcg(\no_g)$.

% \begin{corollary}
%   There exists a unique family of conformal densities $\left\{ \mu_x \right\}_{x \in \teich(\no_g)}$ on the limit set $\pml^+(\no_g)$, given by the Patterson-Sullivan construction.
%   Furthermore, the action of $\mcg(\no_g)$ on $\pml^+(\no_g)$ is ergodic, and the geodesic flow on the restricted cotangent bundle over $\systole(\no_g)$ is mixing with respect to the Bowen-Margulis measure.
% \end{corollary}

% \begin{enumerate}[(i)]
% \item Existence of a unique family of Patterson-Sullivan measures on the limit set $\pml^+(\no_g)$.
% \item Mixing of the geodesic flow on the restricted cotangent bundle over $\systole(\no_g)$.
%   % This can be used to count lattice points in $\teich(\no_g)$.
% \item Ergodicity of the $\mcg(\no_g)$ action on $\pml^+(\no_g)$.
% \end{enumerate}

% Statistical convex-cocompactness is a fairly robust notion for subgroups of the mapping class groups.
% \textcite{gekhtman2023dynamics}, and \textcite{CGTY} show that statistically convex-cocompact actions of subgroups of the mapping class group have good dynamics, namely one can construct a geodesic flow invariant finite measure on the unit cotangent bundle, such that the geodesic flow is mixing with respect to this measure.
% \todo[inline]{Rewrite this paragraph.}

\subsection*{Why we care about Patterson-Sullivan theory for $\mcg(\no_g)$}

\subsubsection*{Counting functions}

Understanding the dynamics of the geodesic flow over the moduli space of \emph{orientable surfaces} has led to solutions for two counting problems: one on the moduli space of orientable hyperbolic surfaces, and one on orientable hyperbolic surfaces themselves.

\begin{enumerate}[(i)]
\item Counting closed curves in moduli space: Via techniques originally introduced to Margulis in his thesis \cite{margulis2004some}, one can reduce counting closed curves, which are conjugacy classes of mapping class group orbit points, to understanding the geodesic flow over the moduli space.
  The number of closed curves of length at most $R$, which we denote by $N(R)$ has the following asymptotics (see \cite{eskinmirzakhani}).
  \begin{align}
    \label{eq:counting-closed}
    N(R) \sim \frac{\exp(hR)}{hR}
  \end{align}
  Here, the symbol $\sim$ means that the ratio of the two quantities approaches a positive constant as $R$ goes to $\infty$, and $h$ is the volume growth entropy of $\teich(\os_{g})$, which is $6g-6$.
\item Counting \emph{simple} closed curves on orientable hyperbolic surfaces: \textcite{mirzakhani2008growth} proved that the counting function $M(R)$ that counts \emph{simple} closed curves satisfies a polynomial asymptotic.
  \begin{align}
    \label{eq:counting-simple-closed}
    M(R) \sim R^{h}
  \end{align}
  Here, $h$ is again the volume growth entropy, i.e.\ $6g-6$.
  % This count also led to an explicit computation of the volumes of moduli spaces of orientable hyperbolic surfaces with boundary, as well as the calculation of expected values for various geometric properties of Weil-Petersson random hyperbolic surfaces.
\end{enumerate}

For non-orientable surfaces, the counting function does not behave like the orientable version.
\textcite{gendulphe2017whats} showed that the counting function $N_{\mathrm{no}}(R)$ and $M_{\mathrm{no}}(R)$, which is the versions of the functions $N(R)$ and $M(R)$ for non-orientable surfaces satisfy the following asymptotic.
\begin{align*}
  N_{\mathrm{no}}(R) &= o\left( \frac{\exp((3g-6)R)}{(3g-6)R} \right) \\
  M_{\mathrm{no}}(R) &= o(R^{3g-6})
\end{align*}
These asymptotics raise the question of whether there is an exponent $h < 3g-6$ for which the non-orientable versions of \eqref{eq:counting-closed} and \eqref{eq:counting-simple-closed} continue to hold.
For $g = 3$, \textcite{10.1093/imrn/rny112} obtained precise asymptotics, and in this case, the growth rate is a non-integer exponent smaller than $3g - 6 = 3$.

If we can upgrade ergodicity of the geodesic flow to mixing of the geodesic flow, we can count lattice points and their conjugacy classes to obtain a non-orientable version of \eqref{eq:counting-closed} where the role of $h$ is played by the critical exponent for the group action of $\mcg(\no_g)$ with respect to the Teichmüller metric.

If the answer to Question \ref{ques:full-scc} is yes, we can use the results of \textcite{CGTY} to establish mixing of the geodesic flow with respect to the Bowen-Margulis measure, and use that to count lattice points.

To explain how ergodicity of the $\mcg(\no_g)$ action on $\pml^+(\no_g)$ might help count simple closed curves on $\no_g$, we outline Mirzakhani's original proof of the fact for orientable surfaces (see \cite{mirzakhani2008growth} for the original proof, and \cite{2022arXiv220204156A} for a gentler exposition).

\begin{proof}[Sketch of simple closed curve counting in the orientable case]
  The proof proceeds in 3 steps.
  \begin{enumerate}[Step 1:]
  \item For any simple closed curve $\gamma$ and any $L > 0$, consider the measure $\mu_L$ on the space $\ml(\os_g)$ of measured laminations.
    \begin{align*}
      \mu_L \coloneqq \frac{1}{L^{6g-6}} \sum_{\alpha \in \mcg(\os_g)} \delta_{\frac{1}{L}\alpha \gamma}
    \end{align*}
  \item Letting $L$ go to $\infty$, $\left\{ \mu_L \right\}$ converges to measure $\mu$ that is $\mcg(\os_g)$-invariant.
    By ergodicity of the $\mcg(\os_g)$-action on $\ml(\os_g)$ with respect to the Thurston measure, we have that the limiting measure $\mu$ is a constant multiple $c$ times the Thurston measure.
  \item To show that the constant $c$ is positive, one needs to average over the moduli space $\mo(\os_g)$, using Mirzakhani's integration formula for the Weil-Petersson volume form.
  \end{enumerate}
\end{proof}

To replicate this proof in the non-orientable setting, we pick the original simple closed curve $\gamma$ to be a \emph{two-sided} curve, and replace the exponent $6g-6$ with $h + 1$, where $h$ is the critical exponent of $\mcg(\no_g)$.
With this replacement, we have the following question.
\begin{question}
  Do the sequence of measures $\mu_L$ converge to a locally finite measure supported on $\ml^+(\no_g)$?
\end{question}

\textcite{erlandsson2023mapping} show that the $\mcg(\no_g)$ orbit closure of such a point indeed is $\ml^+(\no_g)$, but the question about convergence of measures is still open.
Since our results suggest that the $\mcg(\no_g)$ action on $\pml^+(\no_g)$ is ergodic with respect to the Patterson-Sullivan measures (and answering Question \ref{ques:full-scc} would imply ergodicity), we can ask the following questions about the limiting measure $\mu$ as well as the product of the Patterson-Sullivan measures with the Lebesgue measure.
% \begin{question}
%   Is there an $\mcg(\no_g)$ ergodic measure on $\ml^+(\no_g)$ that is absolutely continuous with the product of the Patterson-Sullivan measure and the Lebesgue measure, when $\ml^+(\no_g)$ is identified with $\pml^+(\no_g) \times \mathbb{R}$?
% \end{question}

\begin{question}
  Is the limiting measure $\mu$ absolutely continuous with respect to the ergodic measure on $\ml^+(\no_g)$ obtained by taking a product of Patterson-Sullivan measure and the Lebesgue measure?
\end{question}
If the answer to the question is yes, then one will have completed Step 2 of the proof for non-orientable surfaces.

To make Step 3 work for non-orientable surfaces, one needs to construct a recursive formula for the volumes of $\systole(\no_g)$: this has been done by \textcite{stanford2023mirzakhani}.

% Making Step 3 work for non-orientable surfaces is still open: this would require coming up with a recursive formula for volumes of $\systole(\no_g)$ (or some other finite volume subset), and not all of $\teich(\no_g)$, since that has infinite $\nu_N$-volume.

% While just mixing of the geodesic flow is not strong enough to obtain the error terms for the counting function $N(R)$, exponential mixing is strong enough, and the error terms provide a way to count simple closed curves, and obtain a version of \eqref{eq:counting-simple-closed} for non-orientable surfaces.
% \todo[inline]{State this as a question}

% \todo[inline]{Something about IETs with flips.}

% \subsubsection*{Random non-orientable hyperbolic surfaces} Since the Weil-Petersson volume of $\mo(\os_{g})$ is finite, one can sample a random orientable hyperbolic surface from this space: using the asymptotics for simple closed curves, Mirzakhani computed the expected values of various geometric properties of random hyperbolic surfaces sampled using this distribution, e.g. systole, diameter, Cheeger constant, etc.
% \todo{Maybe get a citation for this, or be more specific?}

% The analogous volume form $\nu_N$ on $\mo(\no_g)$ has infinite mass, and as a result cannot be used to sample a random non-orientable hyperbolic surface.
% However, $\systole(\no_g)$ has finite $\nu_N$-mass, and can be used to sample a random non-orientable hyperbolic surface: if we establish a version of \eqref{eq:counting-simple-closed}, we can hope to compute the expectation of geometrically meaningful random variables over this probability space.

\subsubsection*{Geometric finiteness for mapping class subgroups}

One can think of $\mcg(\no_g)$ as a subgroup of $\mcg(\os_{g-1})$ (where $\os_{g-1}$ is the orientation double cover of $\no_g$), where the embedding is obtained by lifting mapping classes on $\no_g$ to orientation preserving mapping classes on $\os_{g-1}$.
The image of $\mcg(\no_g)$ is an infinite-index subgroup, and stabilizes an isometrically embedded copy of $\teich(\no_g)$ inside $\teich(\os_{g-1})$.

For subgroups of mapping class groups, the notion of convex-cocompactness was introduced by \textcite{farb2002convex}: these groups have good properties with respect to their dynamics on the Teichmüller space.
A natural generalization of these subgroups, inspired by the Kleinian setting, is the notion of geometric finiteness.
While there is not universally agreed upon notion of geometric finiteness for mapping class subgroups, the following two classes are subgroups are considered to be geometrically finite by any reasonable definition.

\begin{enumerate}[(i)]
\item Veech groups: These are stabilizers of Teichmüller discs in $\teich(\os_{g-1})$ which are finitely generated.
  They are lattices in $\mathrm{SL}_2(\mathbb{R})$, and their action on the Teichmüller discs they stabilize is well understood via hyperbolic geometry.
\item Combinations of Veech groups: \textcite{leininger2006combination} show that if two Veech groups $H$ and $K$ share a maximal parabolic subgroup $A$, the subgroup they generate is $H \ast_A K$ (after possibly conjugating by a pseudo-Anosov).
\end{enumerate}

The key emphasis with these two examples is that there are only finitely many cusps, i.e.\ finitely many conjugacy classes of reducible elements.
However, that is not the case for $\mcg(\no_g)$, it stabilizes an isometrically embedded sub-manifold, and yet there are infinitely many conjugacy classes of reducible elements.
Despite having infinitely many ``cusps'', our results show that it is still possible to do Patterson-Sullivan theory on $\mcg(\no_g)$, which is a departure from the Fuchsian/Kleinian setting, where finite Bowen-Margulis measure requires finitely many cusps.

% This suggests that for subgroups of mapping class groups, one can do Patterson-Sullivan theory even for groups that are not considered to be .
% \todo{Maybe go into more detail. Should I even be saying the geometric finiteness is too restrictive. Is that rude?}

\subsection*{Idea behind proofs of main theorems}

In this subsection, we outline the key ideas behind the proof of the main theorems.

\subsubsection*{Weak convexity of $\systole(\no_g)$}
We construct a projection map from $\teich(\no_g)$ to $\systole(\no_g)$ which takes any one-sided curve of length less than $\vept$ and increases its length to $\vept$, while keeping the lengths and twists of other curves constant.
We then use Minsky's product region theorem to show that this projection map increases distance by only a factor of $(1 + \vepd)$, where $\vepd$ can be picked to be arbitrarily small.

\subsubsection*{Statistical convexity of $\systole(\no_g)$}
To show that geodesics in $\systole(\no_g)$ stay away from the thin part, we construct a random walk on $\systole(\no_g)$, and compute the probability of a single step of the random walk entering the thin part, and show that this probability is small.
Estimating this probability reduces to computing an average over a ball in $\mathbb{H}$ because of Minsky's product region theorem.
The random walk argument gives us that the number of geodesics of length at most $R$ entering the thin part is at most $\exp((\hNP - 1)R)$, where $\hNP$ is the discrete analog of the volume growth entropy of $\systole(\no_g)$.
However, the total number of geodesics of length at most $R$ grows like $\exp((\hLP)R)$, where $\hLP$ is the growth rate of the number of lattice points.
To show that the probability of a geodesic entering the thin part is exponentially small, we need to relate the two entropy terms, and show that $\hLP > \hNP - 1$.

\subsubsection*{Showing $\hLP = \hNP$}
We prove entropy equality by inducting on the complexity of the surface.
We first show it for surfaces with Euler characteristic equal to $-1$ using direct methods, and reduce the inductive step to proving an estimate on complexity length for geodesic segments that spend a definite fraction of their time in thin part.

\subsubsection*{Complexity length estimate}

In this section, we
% use the machinery of complexity length introduced by \textcite{dowdall2023lattice} to
show that geodesic segments that spend a small but definite fraction of time near their end in the thin part are rare.
We do this by showing that $\hNP$ for a proper subsurface is strictly smaller than $\hNP$ for the entire surface, and use the machinery of complexity length (due to \textcite{dowdall2023lattice}), which builds upon Minsky's product region theorem and hierarchical hyperbolicity of Teichmüller space, to show that geodesic segments ending in the thin part are rare.

\subsection*{Acknowledgements}

The author would like to thank his advisor Alex Wright for constant support for the duration of this project.
The author would also like to thank Spencer Dowdall, Howard Masur, Kasra Rafi, and Jacob Russell for explaining various aspects of hierarchical hyperbolicity.
The author would also like to thank Ilya Gekhtman for comments on an earlier draft of the paper.
The work done in this paper was supported by the Rackham Predoctoral Fellowship for the academic year 2022-2023.

% {\color{red} Figure out the name of the grant I should thank.}

% \tableofcontents

% \todo[inline]{Find and rewrite all phrases that begin with ``it's easy to see that''.}

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
