\section{The Weak Convex Core of $\teich(\no_g)$}
\label{sec:weak-convex-core}

\subsection{Issues with Geometric Finiteness and Statistical Convex-Cocompactness}
\label{sec:issu-with-geom}

In order to show that the action of $\mcg(\no_g)$ on $\teich(\no_g)$ is geometrically finite (in the sense of Fuchsian groups), we need to exhibit a \emph{convex core}, i.e.\ a convex subset of $\teich(\no_g)$ on which the action of $\mcg(\no_g)$ is finite covolume.
Similarly, to show that the action of $\mcg(\no_g)$ on $\teich(\no_g)$ is statistically convex-cocompact, we need to exhibit a \emph{statistical convex core}, which is a \emph{statistically convex subset} (see Definition \ref{defn:statistical-convex-subset}) of $\teich(\no_g)$ on which $\mcg(\no_g)$ acts cocompactly.

A candidate for the convex core was suggested by \textcite{gendulphe2017whats}, namely the \emph{one-sided systole superlevel set} $\systole(\no_g)$.

\begin{definition}[One-sided systole superlevel set]
  The one-sided systole superlevel set is the subset of $\teich(\no_g)$ where no one-sided curve is shorter than $\vept$. This set is denoted $\systole(\no_g)$.
\end{definition}

The subset $\systole(\no_g)$ has several properties that suggest it should be the convex core for the $\mcg(\no_g)$ action.
\begin{itemize}
\item[-] The space $\teich(\no_g)$ $\mcg(\no_g)$-equivariantly deformation retracts onto the subset $\systole(\no_g)$ (Proposition 19.2 of \cite{gendulphe2017whats}).
\item[-] The $\mcg(\no_g)$ action on $\systole(\no_g)$ has finite $\nu_N$-covolume, where $\nu_N$ is the non-orientable analog of the Weil-Petersson volume form (Proposition 19.1 of \cite{gendulphe2017whats}).
\end{itemize}

However, the subset $\systole(\no_g)$ fails to be convex, in a very strong sense, as we show in a prior paper.
\begin{theorem}[Theorem 5.2 of \cite{limitsetkhan}]
  For all $\vept > 0$, and all $D > 0$, there exists a Teichmüller geodesic segment whose endpoints lie in $\systole(\no_g)$ such that some point in the interior of the geodesic is more than distance $D$ from $\systole(\no_g)$.
\end{theorem}

With this obstruction, we see that $\systole(\no_g)$ will not work as a convex core for a geometrically finite action.
There are two directions one could go in with this obstruction in mind, which we phrase as open questions.

If we wish to show that $\mcg(\no_g)$ acts geometrically finitely, this is the question we need to answer.
\begin{question}
  \label{ques:geom-finite-core}
  Does there exist some other subset of $\teich(\no_g)$ that is finite $\nu_N$-covolume, convex, and an $\mcg(\no_g)$-equivariant deformation retract of $\teich(\no_g)$?
\end{question}
% For instance, one could define a subset $\wt{\systole}(\no_g)$, which is the subset of $\teich(\no_g)$ where the \emph{extremal length} of no one-sided curve is shorter than $\vept$.
% This subset could pos

Alternatively, if we wish to show that $\mcg(\no_g)$ acts statistically convex-cocompactly on $\teich(\no_g)$, where $\thick(\no_g)$ acts as the statistical convex core, this is the question we need to answer.

\begin{question}
  \label{ques:full-stat-core}
  Is $\thick(\no_g)$ statistically convex?
\end{question}

We suspect the answer to Question \ref{ques:full-stat-core} is yes, despite our methods not working.
Our methods for proving statistical convexity rely on proving recurrence of random walks on $\teich(\no_g)$, and random walks on all of $\teich(\no_g)$ have poor recurrence properties when they enter regions where one-sided curves are short.
When the random walks enter these one-sided thin regions, they behave like symmetric random walks on $\mathbb{Z}$, which we know do not have very strong recurrence properties.
We explain this in more detail in Section \ref{sec:why-approach-fails}, when we set up the machinery of Foster-Lyapunov-Margulis functions.

\subsection{A Weaker Notion of Convexity}
\label{sec:weak-noti-conv}

Rather than directly answering questions \ref{ques:geom-finite-core} or \ref{ques:full-stat-core}, we define an even weaker notion of convexity as an intermediate goal.
In the next subsection, we will show that $\systole(\no_g)$ satisfies this weaker notion of convexity.
In this section, we define the notion, and explain why this weaker notion of convexity is still sufficient for the purposes of Patterson-Sullivan theory.

\begin{definition}[Weak convexity]
  A subset $S$ of a geodesic metric space $X$ is said to be $\vepd$-weak convex (for $\vepd > 0$) if there exists a constant $t > 0$ such that for any pair of points $x$ and $y$ in $S$, any geodesic path $\gamma$ joining $x$ and $y$ longer than $t$ can be homotoped to a path $\gamma^{\prime}$ joining $x$ and $y$ such that $\gamma^{\prime}$ lies entirely within $S$, and the lengths of $\gamma$ and $\gamma^{\prime}$ satisfy the following inequality.
  \begin{align*}
    \ell(\gamma^{\prime}) \leq (1 + \vepd) \ell(\gamma)
  \end{align*}
\end{definition}

\begin{remark}
  Strictly speaking, we should call a subset $(\vepd, t)$-weak convex, as the constant $t$ is part of the data that makes a set weak convex.
  However, the constant $t$ will not matter for us, so we suppress it in all mentions of weak convexity.
\end{remark}

An $\vepd$-weak convex subset is a subset which, while not entirely undistorted, has bounded distortion with respect to the ambient metric space at large enough scale.
% When $\vepd = 0$, an $\vepd$-weak convex is an actual convex subset, at least for uniquely geodesic metric spaces.
Weak convexity also interacts well with results from Patterson-Sullivan theory.
Suppose we have a discrete group $G$ acting properly discontinuously on a metric space $X$, and let $X_{\vepd}$ be an $\vepd$-weak convex subset of $X$ upon which $G$ also acts.
If the critical exponent for the $G$ action on $X$ is $\delta$, and the corresponding exponent for $X_{\vepd}$ is $\delta_{\vepd}$, we immediately get the following estimate for $\delta$.
\begin{align*}
  \delta \leq \delta_{\vepd} (1 + \vepd)
\end{align*}

% We can also define a \emph{slowed down geodesic flow} for a subset of the tangent directions on $X_{\vepd}$: namely the tangent directions along which the geodesic enters $X_{\vepd}$ infinitely often in either direction.
% For such bi-infinite geodesics, we can homotope them to lie entirely within $X_{\vepd}$, by only increasing their length by $\vepd$ fraction.
For tangent directions along which the Teichmüller geodesic stays in $\systole(\no_g)$ for arbitrarily large times, we can consider the Teichmüller geodesic flow, and reparameterize the flow speed such that the following equation holds.
\begin{align*}
  d_{\vept}(v, g_{\tau} v) = \tau
\end{align*}
If we can establish mixing results for this reparameterized geodesic flow, we can use the techniques of \textcite{roblin2003ergodicite} to count lattice points in $X_{\vepd}$, the counting results translate into estimates for lattice points in $X$.
\begin{align*}
  \#\left( \text{Lattice points in $X$ within distance $R$} \right) \leq \#\left( \text{Lattice points in $X_{\vepd}$ within distance $R(1 + \vepd)$} \right)
\end{align*}

We can get even better estimates if rather than having a single $\vepd$-weak convex subset, we have an family of subsets, such that the $\vepd$ goes to $0$, and the union of the weak convex subsets is the entire space.

\begin{definition}[Exhaustion by weak convex subsets]
  A metric space $X$ is said to be exhausted by weak convex subsets if there exists a nested family of subsets $\left\{ X_i \right\}$, such that $X_i$ is $\varepsilon_i$-weak convex, where $\varepsilon_i$ goes to $0$, and $\bigcup_{i=1}^{\infty} X_i = X$.
\end{definition}

When there is an exhaustion by weak convex subsets, one can get arbitrarily good bounds for the critical exponent for the $G$ action on $X$.
% , as well as count lattice points on $X$ with only subexponential error terms.

\subsection{Weak Convexity for $\systole(\no_g)$}
\label{sec:weak-conv-syst}

In this section, we will show that $\systole(\no_g)$ is an $\vepd$-weak convex subset of $\teich(\no_g)$, and that $\teich(\no_g)$ can be exhausted by the subsets $\systole(\no_g)$ as $\vept$ goes to $0$.

\begin{theorem}
  \label{thm:weak-convexity}
  For any $\vepd > 0$, there exists a $\vept > 0$ such that $\systole(\no_g)$ is a $\vepd$-weak convex subset of $\teich(\no_g)$.
\end{theorem}

The key ingredient in the proof of Theorem \ref{thm:weak-convexity} is a version of Minsky's product region theorem \cite[Theorem 6.1]{1077244446} for non-orientable surfaces, which we prove in Section \ref{sec:minskys-prod-regi}.

Let $\gamma = \left\{ \gamma_1, \ldots, \gamma_j, \ldots, \gamma_k \right\}$ be a multicurve on a non-orientable surface $\no_g$, where for $i \leq j$, $\gamma_i$ is a two-sided curve, and for $i > j$, $\gamma_i$ is a one-sided curve.
Let $X_\gamma$ denote the metric space obtained as the $\sup$-product $\teich(\no_g \setminus \gamma) \times \mathbb{H}_1 \times \cdots \times \mathbb{H}_j \times (\mathbb{R}_{>0})_{j+1} \times \cdots \times (\mathbb{R}_{>0})_k$, where the $\mathbb{H}_i$ are copies of the upper half plane with the hyperbolic metric, and $\mathbb{R}_{>0}$ is the set of positive real numbers, where the distance between $x$ and $y$ is $\left| \log \left( \frac{x}{y} \right) \right|$.
For any pants decomposition that contains $\gamma$, we consider the Fenchel-Nielsen coordinate systems associated to the pants decomposition.
We have a map $\Pi$ from $\teich(\no_g)$ to $X_\gamma$, which is called the \emph{product region projection map}.
\begin{definition}[Product region projection map]
  The product region projection map $\Pi: \teich(\no_g) \to X_\gamma$ is defined in the following manner.
  \begin{itemize}
  \item The $\teich(\no_g \setminus \gamma)$-coordinate is obtained by setting the lengths to $0$ of all the curves in $\gamma$ to get a punctured hyperbolic surface.
  \item The $\mathbb{H}_i$-coordinate is $\left( t, \frac{1}{\ell} \right)$, where $t$ is the \emph{twist} (i.e. the twist coordinate in the Fenchel-Nielsen coordinate system) of the two-sided curve $\gamma_i$, and $\ell$ is the hyperbolic length.
  \item The $(\mathbb{R}_{>0})_i$ coordinate is $\frac{1}{\ell}$, where $\ell$ is the hyperbolic length of the one-sided curve $\gamma_i$.
  \end{itemize}
\end{definition}

We define a metric on the product $X_\gamma$ as the supremum of the metrics on each of the components, where the metric on $\teich(\no_g \setminus \gamma)$ is the Teichmüller metric, the metric on the $\mathbb{H}_i$ components is the hyperbolic metric, and the metric on the $(\mathbb{R}_{>0})_i$ is given by $d(x,y) = \left| \log\left( \frac{x}{y}  \right) \right| $, i.e.\ the restriction of the hyperbolic metric in $\mathbb{H}$ to a vertical line.

We consider the restriction of $\Pi$ to the thin region of Teichmüller space, denoted $\teich_{\gamma \leq \vept}(\no_g)$, which is the region where all curves in $\gamma$ have hyperbolic length at most $\vept$.

\begingroup
\def\thetheorem{\ref{thm:prno}}
\begin{theorem}[Product region theorem for non-orientable surfaces]
  For any $c >0$, there exists  $\vept^{\prime} > 0$, such that for any $\vept < \vept^{\prime}$, the restriction of $\Pi$ to $\teich_{\gamma \leq \vept}(\no_g)$ is an isometry with additive error at most $c$, i.e.\ the following holds for any $x$ and $y$ in $\teich_{\gamma \leq \vept}(\no_g)$.
  \begin{align*}
    \left| d(x, y) - d_{X_{\gamma}}(\Pi(x), \Pi(y)) \right| \leq c
  \end{align*}

\end{theorem}
\addtocounter{theorem}{-1}
\endgroup

We can now prove Theorem \ref{thm:weak-convexity}.

\begin{proof}[Proof of Theorem \ref{thm:weak-convexity}]
  We begin by picking a small constant $\vept^{\prime} > 0$ and $\delta > 0$.
  We will fix the values of these constants at the end of the proof.
  Let $[x,y]$ be a geodesic segment that starts and ends in $\systolearg{\vept^{\prime}}(\no_g)$.
  Let $\{p_i\}$ be points on $[x,y]$, such that $x = p_0$, $d(p_i, p_{i+1}) = \delta$, and $d(p_n, y) \leq \delta$, where $p_n$ is the last of the $p_i$'s.

  The first step of our proof is modifying the path $[x,y]$ and estimating the length of the modified path.
  We do so by constructing new points $p_i^{\prime}$, where $p_i^{\prime}$ is obtained from $p_i$ by increasing the length of any one-sided curve that is shorter than $\vept^{\prime}$ to $\vept^{\prime}$.
  This ensures that the endpoints of the segments $[p_i^{\prime}, p_{i+1}^{\prime}]$ are in $\systolearg{\vept^{\prime}}(\no_g)$.
  Estimating $d(p_i^{\prime}, p_{i+1}^{\prime})$ splits up into two cases.
  \begin{enumerate}[(i)]
  \item When $p_i = p_i^{\prime}$ and $p_{i+1} = p_{i+1}^{\prime}$: In this case $d(p_i^{\prime}, p_{i+1}^{\prime}) = \delta$, by construction.
  \item When at least one of $p_i$ and $p_{i+1}$ are not equal to $p_i^{\prime}$ and $p_{i+1}^{\prime}$: In this case, we can assume without loss of generality that both $p_i \neq p_i^{\prime}$ and $p_{i+1} \neq p_{i+1}^{\prime}$.
    If that is not the case, and say $p_i \neq p_i^{\prime}$ and $p_{i+1} = p_{i+1}^{\prime}$, we replace $p_{i+1}$ with the last point $y$ on $[p_i, p_{i+1}]$ that is outside $\systolearg{\vept^{\prime}}(\no_g)$.
    The interval $[y, p_{i+1}]$ can be treated as in case (i), and we focus on $[p_i, y]$.

    We have that the interior of $[p_i, p_{i+1}]$ and $[p_i^{\prime}, p_{i+1}^{\prime}]$ both lie in the region where some one-sided curve $\gamma$ is shorter than $\vept^{\prime}$.
    We invoke Theorem \ref{thm:prno} to estimate distances in this region: we have a constant $c(\vept^{\prime})$ that depends on $\vept^{\prime}$ such that following holds.
    \begin{align}
      \label{eq:p-estimate}
      \left| d(p_i, p_{i+1}) - \sup\left( d_{\teich(\no_g \setminus \gamma)}(\Pi(p_i), \Pi(p_{i+1})), \left| \log \left( \frac{\ell_{p_i}(\gamma)}{\ell_{p_{i+1}}(\gamma)}  \right) \right| \right) \right| \leq c(\vept^{\prime})
    \end{align}
    Observe that when we replace $p_i$ by $p_i^{\prime}$ and $p_{i+1}$ by $p_{i+1}^{\prime}$, the first argument $\sup$ stays the same, and the second argument becomes $0$.
    \begin{align}
      \label{eq:p-prime-estimate}
      \left| d(p_i^{\prime}, p_{i+1}^{\prime}) - \sup\left( d_{\teich(\no_g \setminus \gamma)}(\Pi(p_i^{\prime}), \Pi(p_{i+1}^{\prime})), 0 \right) \right| \leq c(\vept^{\prime})
    \end{align}
    This leads to the following estimate for $d(p_i^{\prime}, p_{i+1}^{\prime})$.
    \begin{align}
      \label{eq:length-estimate-homotope}
      d(p_i^{\prime}, p_{i+1}^{\prime}) \leq \delta + 2c(\vept^{\prime})
    \end{align}
  \end{enumerate}
  We construct a new path $\lambda$ by joining $p_i^{\prime}$'s, and $p_n$ to $y$.
  If we let $l$ denote the length of $[x,y]$, we get the following estimate for $\ell(\lambda)$ using \eqref{eq:length-estimate-homotope}.
  \begin{align*}
    \ell(\lambda) \leq l \left( 1 + \frac{2c(\vept^{\prime})}{\delta} \right)
  \end{align*}
  We now pick a value of $\delta$ small enough such that along each of the segments $[p_i, p_{i+1}]$, there is at least one one-sided curve that stays short throughout, and then we pick $\vept^{\prime}$ small enough so that $c(\vept^{\prime})$ is small enough to make $\frac{2c(\vept^{\prime})}{\delta} < \vepd$.

  We now need to show that this new path stays within $\systole(\no_g)$ for some $\vept < \vept^{\prime}$.
  We already have that $x$, $y$ and all the $p_{i}^{\prime}$ are in $\systolearg{\vept^{\prime}}(\no_g)$ and thus in $\systole(\no_g)$.
  For the interior of the geodesic segments $[p_i^{\prime}, p_{i+1}^{\prime}]$, since the endpoints are in $\systolearg{\vept^{\prime}}(\no_g)$, and the length of the segments is no more than $\delta(1 + \vepd)$, we have that there exists some $\vept$ such that $[p_i^{\prime}, p_{i+1}^{\prime}]$ lies in $\systole(\no_g)$.

  Finally, we have to deal with geodesic segments $[w,z]$ which start or end in $\systole(\no_g) \setminus \systolearg{\vept^{\prime}}(\no_g)$.
  We do so by increasing the lengths of short one-sided curves on $w$ and $z$ to $\vept^{\prime}$ if there are any curves shorter than $\vept^{\prime}$.
  Let the modified points be $w^{\prime}$ and $z^{\prime}$: we first construct a path joining $w^{\prime}$ and $z^{\prime}$ that stays within $\systole(\no_g)$ using our construction, and then prepend that path with a path joining $w$ with $w^{\prime}$ and append a path joining $z^{\prime}$ to $z$.
  This new path joining $w$ to $z$ stays entirely withing $\systole(\no_g)$, but we now incur a fixed additive error along with our multiplicative error as well.
  However, if the path is long enough, the additive error can be absorbed in the multiplicative error, with a slightly worse constant.
  We do that, and the threshold for the path being long enough is the constant $t$ that appears in our definition of weak convexity.
  This proves the result.
\end{proof}

\begin{remark}
  We emphasize that the key step in the above proof is going from \eqref{eq:p-estimate} to \eqref{eq:p-prime-estimate}, where the $\log\left( \frac{\ell_{p_i}(\gamma)}{\ell_{p_i^{\prime}}(\gamma)}  \right)$ term becomes $0$.
  This is only possible because there cannot be any twisting around a one-sided curve $\gamma$, so the projection map that sends $p_i$ to $p_i^{\prime}$ and $p_{i+1}$ to $p_{i+1}^{\prime}$ is distance reducing.
  If one tried to use the same proof strategy to show that the thick part of $\teich(\os)$, for any orientable or non-orientable surface $\os$ is weak convex in $\teich(\os)$, the step we described would be the point of failure.
  In particular, if there's a twist along $\gamma$, going from \eqref{eq:p-estimate} to \eqref{eq:p-prime-estimate} will not be distance reducing, and will exponentially increase the distance, leading the estimate to fail.
\end{remark}

Now that we have established that $\systole(\no_g)$ is $\vepd$-weak convex, we can justifiably call it the weak convex core of $\teich(\no_g)$.
For the remainder of this paper, we fix $\vepd < \left(  \frac{1}{6g-12} \right)^2$, and a value of $\vept$ such that $\systole(\no_g)$ is $\vepd$-weak convex.

\begin{definition}[Weak convex core of $\teich(\no_g)$]
  We call $\systole(\no_g)$ the weak convex core of $\teich(\no_g)$, and denote it $\core(\teich(\no_g))$.
  % The specific value of $\vept$ will usually not be important (as long as it is smaller than a threshold value), or clear from context.
\end{definition}

We now also provide a partial classification of the \emph{strongly contracting} elements of $\mcg(\no_g)$ for the metric space $\systole(\no_g)$.

\begin{definition}[Strongly contracting element]
  An infinite order element $\gamma$ in $\mcg(\no_g)$ is said to be strongly contracting if there exists a $p \in \systole(\no_g)$ such that the following two conditions hold.
  \begin{enumerate}[(i)]
  \item $\left\{ \gamma^i p \right\}_{i \in \mathbb{Z}}$ quasi-isometrically embeds in $\systole(\no_g)$.
  \item For any ball of radius $R$ disjoint from $\left\{ \gamma^i p \right\}$, its projection onto $\left\{ \gamma^i p \right\}$ has uniformly bounded diameter.
  \end{enumerate}
\end{definition}

\begin{lemma}[Partial classification of strongly contracting elements]
  \label{lem:strongly-contract-class}
  Let $\gamma$ be an infinite order element in $\mcg(\no_g)$.
  \begin{enumerate}[(i)]
  \item If $\gamma$ is pseudo-Anosov, then $\gamma$ is strongly contracting.
  \item If $\gamma$ leaves a two-sided curve invariant, then $\gamma$ is not strongly contracting.
  \end{enumerate}
\end{lemma}

\begin{proof}
  We deal with the two cases separately.
  \begin{description}
  \item[Case (i)] In this case, we pick $p$ to lie along the axis of the pseudo-Anosov $\gamma$.
    Passing to the orientable double cover, we have that the projection of any ball disjoint from the axis has bounded diameter, by \textcite{minsky1996quasi}.
    Since $\teich(\no_g)$ isometrically embeds inside the Teichmüller space of the double cover, we have the claim for $\teich(\no_g)$.
    To show now that the result holds for $\systole(\no_g)$, observe that the induced metric on $\systole(\no_g)$ is minimally distorted from the metric on $\teich(\no_g)$, by Theorem \ref{thm:weak-convexity}.
    One of two things can happen: the axis of $\gamma$ lies in $\systole(\no_g)$, or it lies outside.
    In the first case, we project as usual, and by Theorem \ref{thm:weak-convexity}, the size of the projection increases by a bounded multiplicative factor.
    In the second case, we first create a new axis, by projecting the old axis onto $\systole(\no_g)$.
    We then get a projection of a ball by first projecting to the old axis, and then composing that with the second projection.
    This composed projection still has bounded diameter because the first projection does, and the second projection increases distances by a bounded multiplicative factor.
  \item[Case (ii)] In this case, we need to show there is no choice of $p$ such that the projection onto $\left\{ \gamma^i p \right\}$ has bounded diameter.
    Suppose there is such a $p$: we will construct a family of balls disjoint from $\gamma$ with arbitrarily large projections onto $\gamma$.
    We can assume without loss of generality that at $p$, one of the invariant two-sided is short.
    If not, we can create a new point $p^{\prime}$ where this is the case, and the orbits $\left\{ \gamma^i p \right\}$ and $\left\{ \gamma^i p^{\prime} \right\}$ have unbounded projections onto each other, and if a family of balls has unbounded projections on $\left\{ \gamma^i p^{\prime} \right\}$, it will also have unbounded projections on $\left\{ \gamma^i p \right\}$.

    Since we have that some two-sided curve $\kappa$ is short at $p$, and $\gamma$ leaves $\kappa$ invariant, we have that the entire orbit $\left\{ \gamma^i p \right\}$ lies in the product region associated to $\kappa$.
    In this product region, it is easy to verify that the projection of a ball of radius $R$ disjoint from $\left\{ \gamma^i p \right\}$ will have projection diameter approximately $2R$, by Minsky's product region theorem.
  \end{description}
  This proves the theorem in the two cases we specified.
\end{proof}

\begin{remark}
  The only case the above classification does not deal with is the case where $\gamma$ is a pseudo-Anosov on a subsurface that is the complement of only one-sided curves.
\end{remark}

%%% Local Variables:
%%% TeX-master: "main"
%%% End: